Surrogate Regret Bounds for Polyhedral Losses

### 2021-05-27 rates-neurips-21/rates.tex

\subsection{Examples}
\bo{TODO}

\bo{Observe that our theory gives some useful way to compare link functions that may not have existed before, i.e. bigger $\epsilon$ seems to be better. Full stop?}

\section{Broader Impacts}
As a theoretical work, this papers' impacts are mostly in the form of downstream research and applications.
Instead of direct applications, we anticipate this work leading to more investigation of surrogate losses to improve discrete prediction tasks.
Of course, such machine learning tasks can be solved for ethical or unethical purposes.
We do not know of particular risk of unethical use of this work more so than general supervised machine learning.

>>>>

\subsection{Further tightening}
While our goal is not to focus on exact constants for specific problems, we remark on a few ways Theorem \ref{thm:separated-constant} may be loose and how one could compute the tightest possible constant $\alpha^*$ for which $R_{\ell}(\psi \circ h;\D) \leq \alpha^* R_L(h;\D)$ for all $h$ and $\D$.
In general, for a fixed $p$, there is some smallest $\alpha_p^*$ such that $R_{\ell}(\psi(u),p) \leq \alpha_p^* R_L(u,p)$ for all $u$.
It is clear that $\alpha^* = \max_{p \in \mathcal{Q}} \alpha_p^*$ for the finite set $\mathcal{Q}$ used in the proof, i.e. the vertices of the full-dimensional level sets of $\Gamma = \prop{L}$.

Above, we bounded $\alpha_p^* \leq \frac{C_{\ell} H_{L,p}}{\epsilon_{\psi}}$.
The intuition is that some $u$ at distance $\geq \epsilon_{\psi}$ from $\Gamma(p)$, the optimal set, may link to a ``bad'' report $r = \psi(u) \not\in \gamma(p)$.
The rate at which $L$ grows is at least $H_{L,p}$, so the surrogate loss at $u$ may be as small as $\frac{\epsilon_{\psi}}{H_{L,p}}$, while the target loss may be as high as $C_{\ell}$.

The tightest possible bound, on the other hand, is $\alpha^* = \sup_{u: \psi(u) \not\in \gamma(p)} \frac{R_{\ell}(\psi(u),p)}{R_L(u,p)}$.
This can be smaller if the values of numerator and denominator are correlated across $u$.
For example, $u$ may only be as close to the optimal set as $\epsilon_{\psi}$ when it links to reports $\psi(u)$ with lower target regret; or $L$ may have a smaller slope in the direction where the link's separation is larger than $\epsilon$.

To illustrate with a concrete example, consider the REB surrogate of \cite{ramaswamy2018} for the abstain loss, $\ell(r,y) = \frac{1}{2}$ if $r = \bot$, otherwise $\ell(r,y) = \ones[r \neq y]$.
\bo{TODO finish}

\paragraph{Different norms.}
\bo{Perhaps mention.}

\section{Broader Impacts}
As a theoretical work, this papers' impacts are mostly in the form of downstream research and applications.
Instead of direct applications, we anticipate this work leading to more investigation of surrogate losses to improve discrete prediction tasks.
Of course, such machine learning tasks can be solved for ethical or unethical purposes.
We do not know of particular risk of unethical use of this work more so than general supervised machine learning.
\bo{Make this more positive: we will broadly impact the world to be happier.}
